%====================
% PROJECT Doctor-online
%====================
\subsection{Doctor-Online (\href{https://play.google.com/store/apps/details?id=com.banna.doctoronline}{Google Play})}
\begin{zitemize}
\item Contributed to the development of a healthcare application offering on-demand medical consultations, appointment scheduling, and access to free medical articles.
\item Integrated Firebase and RESTful APIs to enable seamless communication between users and healthcare professionals.

\end{zitemize}


%====================
% PROJECT Euro
%====================
\subsection{Euro Club Rescue Service (\href{https://play.google.com/store/apps/details?id=com.euroclub.rescue}{Google Play})}
\begin{zitemize}
\item Developed a mobile application for emergency assistance and rescue services, providing users with features such as roadside assistance, towing services, and more.
\item Integrated Google Maps

\end{zitemize}

%====================
% PROJECT Nutrition Hub
%====================
\subsection{Nutrition Hub (\href{https://apps.apple.com/eg/app/\%D9\%85\%D8\%B1\%D9\%83\%D8\%B2-\%D8\%A7\%D9\%84\%D8\%AA\%D8\%BA\%D8\%B0\%D9\%8A\%D8\%A9-nutrition-hub/id6475817915}{App Store})}
\begin{zitemize}
\item Contributed to the development of an iOS application focused on nutrition and diet management, offering users personalized meal plans, nutritional advice, and tracking tools.
\item Collaborated on integrating local storage for user data and optimized the app for smooth performance and user experience.
\end{zitemize}


%====================
% PROJECT shopink
%====================
\subsection{Shopink (\href{https://github.com/Allam-dev/TEKNOSOFT}{Repo})}
\begin{zitemize}
\item Developed a comprehensive e-commerce mobile application designed to offer seamless shopping experiences with features like product browsing, user authentication, and secure payment integration.
\item Integrated Firebase for user authentication, real-time database updates, and cloud storage, providing a robust backend solution.
\item Incorporated RESTful APIs to manage product information, order processing, and payment gateway interactions.
\end{zitemize}


%====================
% PROJECT D
%====================
% \subsection{\href{https://pinsave-by-ray.onrender.com/}{Pinsave} \href{https://github.com/thekiranmahajan/pinsave}{\{Repo\}} \hfill Dec 2023 --- Jan 2024}
% \begin{zitemize}
% \item Constructed a Pinterest-like web app with \textbf{JavaScript}, \textbf{Tailwind CSS}, \textbf{EJs}, \textbf{Node.js}, and \textbf{Express.js}.
% \item Implemented \textbf{Authentication Authorization} via Passport for user access control and dynamic feed retrieval.
% \item Engineered image-based post creation and real-time updates with \textbf{responsive design}.
% \item Deployed on \textbf{Render} with \textbf{MongoDB} integration, also added error handling and default image logic for scalability.
% \end{zitemize}